Improved Bounds for Online Balanced Repartitioning

### 2020-05-01 paper/disc20clustering.tex
k=3

\subsection{Distributed implementation of $k=2$ algorithm}

For a repartition, it is sufficient to find the cluster with the signature $1,1,1$. 
We call any such cluster \emph{X (todo name)}.
Idea of distributed implementation of this procedure:
\begin{enumerate}
	\item Assign ids to clusters and order them
	\item Recursively partition clusters into two groups
	\item Each group maintains the pointer to a subgroup that contains at least one X cluster; a pointer may be null (then no X there)
	\item This way, finding a cluster X requires $\log_2(\ell)$ communication
	\item After removing an X cluster, we need to fix the pointers. This is done by following the path from the removed X cluster to the root. We simply ask the sibling if it contains X.
\end{enumerate}

\maciek{How to distribute our algorithms: PPL, k=2 and DET}

>>>>

\subsection{Distributed implementation of $k=3$ algorithm}

For a repartition, it is sufficient to find the cluster with the signature $1,1,1$. 
We call any such cluster \emph{X (todo name)}.
Idea of distributed implementation of this procedure:
\begin{enumerate}
	\item Assign ids to clusters and order them
	\item Recursively partition clusters into two groups
	\item Each group maintains the pointer to a subgroup that contains at least one X cluster; a pointer may be null (then no X there)
	\item This way, finding a cluster X requires $\log_2(\ell)$ communication
	\item After removing an X cluster, we need to fix the pointers. This is done by following the path from the removed X cluster to the root. We simply ask the sibling if it contains X.
	\item Possible improvement: we can have a fixed number of rounds for finding the X cluster by maintaining a direct pointer to an X cluster (not only to subgroup). However, the fix still requires the log number of rounds. But we improved the responsiveness.
\end{enumerate}

\maciek{How to distribute algorithms: PPL and DET}
